%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}


\name{Andreas Pålsson} % Your name
\address{David Bagares Gata 6 \\ 111 38 Stockholm} % Your address
\address{(46)~$\cdot$~708952853 \\ apals@kth.se} % Your phone number and email
\rhead{2015-01-06}
\pagenumbering{gobble}
\begin{document}


%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf KTH Royal Institute of Technology, Stockholm} \hfill {\em 2012-2017} \\ 
Currently studying my fourth year of Computer Science and Engineering.

Projects include, among others, a chat- and eventsystem written in Unity3D for the adventure game Dynastica \textit{(http://dynastica.com)}

{\bf Rose-Hulman Institute of Technology, Indiana} \hfill {\em 2014-2015} \\ 
Took classes in artificial intelligence, operating systems and discrete mathematics.

Projects include a minimalist operating system written in ANSI C, including functionality regarding interrupt handling, memory management and multiprocessing. I also developed an Android application to calculate and display all connected users' caffeine level in real-time. 

{\bf Natural sciences, mathematics and computer science, Nacka Gymnasium} \hfill {\em 2010-2012} \\ 
Graduated with the highest possible grade in all subjects and was awarded a scholarship due to my academic performances.

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Söderberg \& Partners}{April 2014 - Present}{System Developer}{Stockholm, Sweden}
\item During the semesters I work part time as the sole developer of the Söderberg \& Partners Android Application, having full responsibility for the Android platform specific design and implementation. The application provides functionality for reporting worked hours, viewing payslips and tracking investments.

\end{rSubsection}

\begin{rSubsection}{THS Armada}{April 2015 - December 2015}{Android Application Developer}{Stockholm, Sweden}
\item I worked with the development of the Android application to be used at KTH's career fair. The fair is annually visited by over 11 000 students and more than 170 companies. The application is designed according to Google's Material design principles and increased visitor engagement at the fair.
\end{rSubsection}

\begin{rSubsection}{Baltic Spot}{Summer 2012, 2013}{Program Developer}{Stockholm, Sweden}
\item During the summer of 2012 I worked full time developing pathfinding software on ocean maps. During 2013 I wrote a report on how the development of the software should proceed and looked for bugs in one of the company's programs.

\end{rSubsection}
\end{rSection}

\begin{rSection}{OTHER MERITS}

\begin{rSubsection}{Teenager of Älta}{June 2009}{}{Stockholm, Sweden}
\item Älta Lions awarded me a scholarship and appointed me Teenager of Älta for my academic performances.
\end{rSubsection}

\begin{rSubsection}{Swedish National Champion, Running}{April 2010}{}{Stockholm, Sweden}
\item Won the team competition at the junior national championships with Spårvägens FK.
\end{rSubsection}


References available upon request
\end{rSection}

%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Technical Strengths}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Computer Languages & Java, Python, R, JavaScript, C++, Ruby, Node.js, LaTeX \\
% Frameworks & Rails, Angular \\
% Protocols \& APIs & JSON, REST \\
% Databases & MongoDB, MySQL, PostgreSQL \\
% \end{tabular}
% \\
% {\em Further knowledge in many programming languages and technological fields.}

% \end{rSection}

\end{document}
